\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
revising sect 6

All traversables (lanes and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. A collision is detected when two agents
reverse order after a time step has completed.
\commentpk{Also do we still have point vehicles only?}
\commentd{Technically yes, but we could add in a check to make sure the fronts
  of every vehicle aren't too close to any other vehicle. It would just be
  needlessly expensive, and we trust the following-distance behavior.}

@@

\commentd{So is this paragraph below still relevant?}
The default behavior maximizes acceleration while obeying speed limits,
avoiding collisions, and obeying intersections. By considering the highest speed
achievable at the end of the next step and the subsequent stopping distance at
this speed, the behavior's lookahead engine can scan sufficiently far ahead
along several traversables to locate agents to avoid and intersections to query.
The analysis short-circuits at the first nearby agent and intersection requiring
a stop, since it would be illegal to drive further anyway.

@@

Picking accelerations that optimize objective functions is a separate task from
picking a path to travel. Agent behaviors consult a route strategy to pick
turns. Currently two simple implementations are available. One statically plans
a route to some goal using standard A* search \cite{astar}. The other performs a
drunken walk, lazily planning random choices at each intersection as the
lookahead engine requires, choosing the direction that minimizes the Euclidean
distance to the goal with 75\% probability. Researchers can experiment with
dynamic replanning or hierarchial planning without modifying any code other than
creating a new route implementation. Route policies could also interact with a
singleton overseer to gain some sort of global insight or with smart
intersections to avoid congestion.

@@

A particular focus of AORTA is intersection policies. To demonstrate how much
policy affects agent performance, three policies are evaluated: stop sign,
traffic signal, and autonomous reservation. These are compared with all other
parameters fixed:

@@

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs propagates timings with a breadth-first search. The goal is
to synchronize green signals so agents in some lanes do not stop for several
intersections.

@@

Each policy has its trade-offs in terms of performance and physical hardware
cost, suggesting a mixed approach, perhaps with intersection policies adapting
as traffic conditions shift. Researchers could conduct this experiment and many
others without needing to understand most of AORTA's code-base. The largest
intersection policy, traffic signals with the flooding heuristic for timing
assignment, is only 400 lines of Scala.

>>>>

All traversables (lanes and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. A collision is detected when two agents
reverse order after a time step has completed.

@@

@@

To pick turns, agent behaviors consult a route strategy. Two simple
implementations exist already: a static route using A* \cite{astar} and a
drunken walk that probabilistically moves towards the destination.  Researchers
can experiment with dynamic replanning or hierarchial planning without modifying
any code other than creating a new route implementation. Route policies could
also interact with a singleton overseer to gain some sort of global insight or
with smart intersections to avoid congestion.

@@

A particular focus of AORTA is intersection policies. To demonstrate how much
policy affects agent performance \commentd{performance is a vague term, but I
don't want to talk about dependent vars just yet}, three policies are evaluated: stop sign,
traffic signal, and autonomous reservation. These are compared with all other
parameters fixed:

@@

The traffic signal policy requires timings and groups of simultaneous turns for
each intersection. The heuristic evaluated uses standard turn groups (turns from
parallel incoming directions are scheduled simultaneously, and left turns are
grouped) and employs breadth-first search to propagate timings. The goal is to
synchronize green signals so agents in some lanes do not stop for several
intersections.

@@

Each policy has its trade-offs in terms of performance and physical hardware
cost \commentd{do we want to raise this issue?}, suggesting a mixed approach,
perhaps with intersection policies adapting as traffic conditions shift.
Researchers could conduct this experiment and many others without needing to
understand most of AORTA's code-base. The largest intersection policy, traffic
signals with the flooding heuristic for timing assignment, is only 400 lines of
Scala.
